|

### 2025-04-03 posts/Horton/Horton2025_slides.qmd
correceted bib file location in Horton2025_slides.qmd

---
title: |
  | John J. Horton
  | Price floors and employer preferences: 
  | Evidence from a minimum wage experiment
subtitle: |
  | *American Economic Review*, 2025, vol. 115, No. 1
author: "Seiro Ito"
engine: knitr
format:
  revealjs: 
    standalone: true
    embed-resources: true
    slide-number: true
    width: 1600
    height: 900
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/Horton/Horton2025_slides.html>
    theme: sky
lightbox: auto
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
bibliography: ../../../../../seiro.bib
#### If it is 2 levels up, ../../seiro.bib
resources:
  - Horton2025_slides.pdf
#### quarto render Horton2025_slides.qmd
---
<style>
:root{--r-main-font-size: 36px;}
.reveal h1, .reveal h2, .reveal h3, .reveal h4, .reveal h5 {
              text-transform: none;
      }
.spacer {
    margin-top: 20px;
}
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>

>>>>

---
title: |
  | John J. Horton
  | Price floors and employer preferences: 
  | Evidence from a minimum wage experiment
subtitle: |
  | *American Economic Review*, 2025, vol. 115, No. 1
author: "Seiro Ito"
engine: knitr
format:
  revealjs: 
    standalone: true
    embed-resources: true
    slide-number: true
    width: 1600
    height: 900
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/Horton/Horton2025_slides.html>
    theme: sky
lightbox: auto
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
bibliography: ../seiro.bib
#### If it is 2 levels up, ../../seiro.bib
resources:
  - Horton2025_slides.pdf
#### quarto render Horton2025_slides.qmd
---
<style>
:root{--r-main-font-size: 36px;}
.reveal h1, .reveal h2, .reveal h3, .reveal h4, .reveal h5 {
              text-transform: none;
      }
.spacer {
    margin-top: 20px;
}
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>
